Visualizing Independence Using Extended Association and Mosaic Plots

### 2003-04-04 trunk/vcd/paper/draft.Rnw
*** empty log message ***
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@234 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
fix to pass R CMD check
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@244 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[10pt]{article}
\usepackage{color, natbib, graphicx}
\usepackage{dsc2003}

@@

\title{Visualizing Independence Using Extended Association and Mosaic Plots}
\author{\hfill David Meyer$^\dag$ \hfill Achim Zeileis$^\dag$ \hfill Kurt Hornik$^\ddag$ \hfill \hfill \\[0.2cm]
\dag {\it \small Institut f\"ur Statistik \& Wahrscheinlichkeitstheorie,
 Technische Universit\"at Wien}\\
\ddag {\it \small Institut f\"ur Statistik, Wirtschaftsuniversit\"at Wien}
}

\maketitle

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}

>>>>

\documentclass[10pt]{article}
\usepackage{Sweave, graphicx}
\usepackage{Z}

@@

\title{Visualizing Independence Using Extended Association and Mosaic Plots}
\author{\hfill Achim Zeileis$^\dag$ \hfill David Meyer$^\dag$ \hfill Kurt Hornik$^\ddag$ \hfill \hfill \\[0.2cm]
\dag {\it \small Institut f\"ur Statistik \& Wahrscheinlichkeitstheorie,
 Technische Universit\"at Wien}\\
\ddag {\it \small Institut f\"ur Statistik, Wirtschaftsuniversit\"at Wien}
}
\date{}
\maketitle

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
grid.mosaicpairs(UCBAdmissions, type = "conditional", gp = gp.shading, main = NULL)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}
